Appendix to ``Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis''

### 2016-11-19 MHCpaper/MHCsupp.tex
changing precision of xpot fitting

We model the \KO\ mice by changing $\M\dep\wt$ to $\M\dep\ko$, which has larger off-diagonal matrix elements.
This reduces the typical number of candidate depression events required to induce a change in synaptic weight, modelling the observed lower threshold for LTD \cite{McConnell2009MHCcerebellum}.

>>>>

We model the \KO\ mice by changing $\M\dep\wt$ to $\M\dep\ko$, which has larger off-diagonal matrix elements.
This makes it easier to induce a decrease in synaptic weight, modelling the observed lower threshold for LTD \cite{McConnell2009MHCcerebellum}.
